Networked Character Devices

### 2011-12-11 report/paper.tex
paper: protocol implementation

>>>>

\lstinputlisting[
  caption={The structures which make up the NCD protocol.},
  label=lst:protocol
]{protocol.c}

The protocol for NCD operates over TCP sockets. Despite the potential
for large amounts of streaming data over the internet --- data which may
be acceptable to drop --- some messages are unacceptable to lose. Any
request or reply should be guaranteed. The data following a
\texttt{read()} or \texttt{write()} (figure \ref{fig:protocol}), for
example, may not be as important. Therefore, in the future it may be
beneficial to implement the core protocol over TCP and bulk data over
UDP (section \ref{sec:futurework}).

Because there is only one type of packet for a request, and another for
a reply, (listing \ref{lst:protocol}) there is a small amount of wasted
space on some file operations. We have done our best to reduce this
overhead as much as possible, making use of a cascade of nested unions
and structs.

The request struct is suitable to handle all of the function arguments
for all of the operations we support. The reply struct is much simpler
as functions only have a single return value. While some file operations
have output parameters and some userspace system calls do as well, there
aren't any cases where these need to be passed over the network.
